---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countr

<!-- badges: start -->

<!-- badges: end -->

The goal of `countr` is to make generating summary tables more
efficient! It contains functions to help you save time in your
exploratory data analysis. Presently, the package contains a function to
count missing values in columns by group, outputting a summary tibble of
missing value counts.

## Installation

You can install the development version of `countr` from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/countr", ref = "0.1.0")
```

## Usage

One of the first steps in any exploratory data analysis is generating
summary tables that help you visualize the structure and quality of your
datasets. For example, a common first step is evaluating the proportion
of values missing for each of your variables in a dataset. This package
includes a function that can quickly create a summary table of missing
value counts.

## Examples

For example, let's see how to count up all the missing values in the
`airquality` dataset by the `Month` variable:

```{r example}
# load the package
library(countr)

# run the function with the airquality dataset
count_all_missing_by_group(airquality, Month) 
```

Alternatively, you could pipe your dataset directly into the function
using the base R pipe, `|>`, or the magrittr pipe `%>%`:

```{r}
# run the function using the pipe with the airquality dataset
airquality |> count_all_missing_by_group(Month)
```

Finally, if you want your output tibble to remain grouped, specify the
`.groups` argument:

```{r}
# specify the .groups argument
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
